Small Case: Checking Hitting Times in the Year of Our Lord

### 2025-02-25 small_case.qmd
Update some progress

ax = sns.ecdfplot(cleaned_metrics, x='hitting_time', hue='nchains', palette=colormaps.get('jet'))

@@

ax.set_xscale('log')
ax.set_xlim(left=0.3, right=3e3)
```

We see relatively good agreement here.
<!-- We detected a bug in this sequence, where the silent graceful failure of numpy.random.Generator.multinomial causes a bug where the transition probabilities that were not normalised correctly earlier cause high probability moves to the "last" node. -->

>>>>

fig, axz = plt.subplots(nrows=2)
axs = axz.flatten()

for ax in axs:
  sns.ecdfplot(
    cleaned_metrics, 
    x='hitting_time', 
    hue='nchains', 
    palette=colormaps.get('jet'),
    ax=ax
  )

@@

axs[1].set_xlim(-10, 100)

```

We see relatively good agreement here.

### Aside: the Bug

We detected a bug in this work, where the silent graceful failure of numpy.random.Generator.multinomial causes a bug where the transition probabilities that were not normalised correctly earlier cause high probability moves to the "last" node.

This causes the ECDFs to clump, and be differentiated by their hitting probabilities.

```{python}
bug_metrics = pl.read_parquet("small_case/metrics_prebug.parquet")
hitting_time_cols = pl.selectors.starts_with('hitting_time_')
aggregated_bugmetrics = bug_metrics.unpivot(
  on=hitting_time_cols,
  index=['nchains','seed',],
  variable_name='target',
  value_name='hitting_time',
)
cleaned_bugmetrics = aggregated_bugmetrics.fill_nan(max_value_plus_one).fill_null(max_value_plus_one)

ax = sns.ecdfplot(cleaned_bugmetrics, x='hitting_time', hue='nchains', palette=colormaps.get('jet'))
```
